\Title

### 2022-09-15 Grimaldi-etal-BiolCybernetics.tex
scan pass

Such recurrent activity would be essential for implementing predictive or anticipatory processes. This is essential in a neural system as it contains multiple different delays that require temporal alignment~\citep{hogendoorn_predictive_2019}. This has been previously modeled to explain for example the flash-lag illusion~\citep{khoei_flash-lag_2017}. \note{Say that this could be implemented by properly setting the timing of the label} As previously stated, this could be implemented using generalized coordinates (that is variables such as position which are complemented by speed, acceleration, jerk, ...) and ``neurobiologically, the application of delay operators just means changing synaptic connection strengths to take different mixtures of generalized sensations and their prediction errors''~\citep{perrinet_active_2014}. Our proposed hetero-synaptic model provides an alternate and elegant implementation solution to this problem.
%
\subsection{Perspectives}
%%%-----------------------------------------------------------------
In the definition of our task, we highlighted how the generation of events depends on the spatial gradient in each image. This gradient is defined in both horizontal and vertical dimensions and its maxima are generally oriented. Taken together, these oriented edges form the contours of visual objects in the scene~\citep{koenderink_representation_1987}. Thus, there is a dependence within the event stream between motion and orientation information. It would be crucial to study this interdependence further. This could be initiated by training the model on a dataset with orientation labels. Studying this dependence will allow us to dissociate these two forms of visual information and to enable us to integrate them. In particular it will allow us to consider that the definition of motion is more accurate perpendicular to an oriented contour (aka, the aperture problem), thus allowing us to implement recurrent predictive rules, such as those identified to dissociate this problem~\citep{perrinet_motion-based_2012}.

The model is trained on a low-level local motion detection task, and one might wonder if it could be trained on higher-level tasks. An example task would be depth estimation in the visual scene. There are multiple sources of information for inferring depth, such as binocular disparity or changes in texture or shading, but in our case, motion parallax would be the most significant cue (Rogers). This is because objects close to an observer move relatively faster on the retina than an object at a great distance. Using this information, one can segment objects and estimate their depth~\citep{yoonessi_contribution_2011}. However, this would first require computing the optical flow. A possible implementation is therefore to add a new layer to our model, in analogy with the hierarchical organization highlighted in the visual cortex. This is theoretically possible by using the output of our model (which estimates velocity in retinotopic space) as input to a new layer of neurons that would estimate velocity in the visual field, including the depth dimension as an output label. This could have direct and important applications, for example in autonomous driving, to detect obstacles in a fast and robust way. Another extension would be to actively generate sensor movements (physically or virtually) to yield better depths estimates notably to resolve uncertain estimates~\citep{nawrot_eye_2003}.

>>>>

Such recurrent activity would be essential for implementing predictive or anticipatory processes. This is essential in a neural system as it contains multiple different delays that require temporal alignment~\citep{hogendoorn_predictive_2019}. This has been previously modeled to explain for example the flash-lag illusion~\citep{khoei_flash-lag_2017}. \note{Say that this could be implemented by properly setting the timing of the label} As previously stated, this could be implemented using generalized coordinates (that is variables such as position which are complemented by speed, acceleration, jerk, ...) and ``neurobiologically, the application of delay operators just means changing synaptic connection strengths to take different mixtures of generalized sensations and their prediction errors''~\citep{perrinet_active_2014}. Our proposed hetero-synaptic model provides an alternate and elegant implementation solution to this problem.
%
\subsection{Perspectives}
%%%-----------------------------------------------------------------
In the definition of our task, we highlighted how the generation of events depends on the spatial gradient in each image. This gradient is defined in both horizontal and vertical dimensions and its maxima are generally oriented. Taken together, these oriented edges form the contours of visual objects in the scene~\citep{koenderink_representation_1987}. Thus, there is a dependence within the event stream between motion and orientation information. It would be crucial to study this interdependence further. This could be initiated by training the model on a dataset with labels providing local orientation. \note{we can say we tried and that it works well}. Studying this dependence will allow us to dissociate these two forms of visual information and to enable us to integrate them. In particular it will allow us to consider that the definition of motion is more accurate perpendicular to an oriented contour (aka, the aperture problem), thus allowing us to implement recurrent predictive rules, such as those identified to dissociate this problem~\citep{perrinet_motion-based_2012}.

The model is trained on a low-level local motion detection task, and one might wonder if it could be trained on higher-level tasks. An example task would be depth estimation in the visual scene. There are multiple sources of information for inferring depth, such as binocular disparity or changes in texture or shading, but in our case, motion parallax would be the most significant cue~\citep{} (Rogers). This is because objects close to an observer move relatively faster on the retina than an object at a great distance. Using this information, one can segment objects and estimate their depth~\citep{yoonessi_contribution_2011}. However, this would require computing first the optical flow. A possible implementation is therefore to add a new layer to our model, in analogy with the hierarchical organization highlighted in the visual cortex. This is theoretically possible by using the output of our model (which estimates velocity in retinotopic space) as input to a new layer of neurons that would estimate velocity in the visual field, including the depth dimension in the output supervision labels. This could have direct and important applications, for example in autonomous driving, to detect obstacles in a fast and robust way. Another extension would be to actively generate sensor movements (physically or virtually) to yield better depths estimates notably to resolve uncertain estimates~\citep{nawrot_eye_2003}.
